---
title: "Problem Set 8"
author: "Rebecca Xi"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipens = 100)

# Here I read in the necessary data. I load the trump_approval_poll from the
# fivethirtyeight package and use the readr package to read in the new tweets
# Rdata file. this repo’s “raw-data” folder.

library(fivethirtyeight)
library(readr)
library(skimr)
library(ggplot2)
library(broom)
library(gt)
library(patchwork)
library(tidyverse)

poll <- trump_approval_poll
load(file = 'raw-data/tweetsnew.Rdata')
```

## Question 1: Conduct exploratory data analysis

### 1A) Summary Statistics

```{r 1A, echo=FALSE}

# Here I group the tweet data by week and create a "total_tweets" variable,
# recording the number of tweets that week (including retweets). This amounts to
# counting the number of tweets per week and renaming the automatic "n" column
# to the desired "total_tweets". Since all we care about is the tweet count,
# discarding the other variables from the original tweets dataset is fine.

tweets_summarized <- tweets %>% 
  group_by(week) %>% 
  count() %>% 
  rename(total_tweets = n)

# I then use the code from the problem set instructions to create a week
# variable in the other dataset, poll. This is to facilitate joining the
# summarized tweet data to the poll database.

poll$week <- ceiling(
  as.numeric(difftime(poll$end_date, "2017-01-01", units = "days")) / 7
)

# Now I join the tweet data to the poll data using the week variable, using
# left_join with poll listed first. The joined tibble has 4929 observations. I
# also use mutate() to assign total_tweets = 0 for weeks where there aren't any
# tweets in the database, replacing any NAs.

tibble <- poll %>% 
  left_join(tweets_summarized, by = "week") %>% 
  mutate(total_tweets = ifelse(is.na(total_tweets), 0, total_tweets))

# Finally, I print the output of calling skim() on the total_tweets and approve
# variables. These will be the two variables of interest when we move on to
# correlations.

skim(tibble$total_tweets)
skim(tibble$approve)
```


### 1B) Bivariate correlations

```{r 1B, echo=FALSE}

# I want to replicate the plot from the problem set instructions, which displays
# the approval rating vs. the tweet count for each week, colored in by grade. I
# learned out how to use fct_explicit_na from
# https://github.com/tidyverse/forcats/issues/122, in order to make any NA
# values of grade explicit so as to not omit them from the plot, and I do this
# separately from the plot code so that the tibble is all set for the rest of
# the problem set. As usual, I apply theme_classic() and the appropriate titles
# and axis labels to describe the plot.

tibble <- tibble %>% 
  mutate_if(is.factor, fct_explicit_na, na_level = "(Missing)")

plot <- tibble %>% 
  ggplot(aes(x = total_tweets, y = approve, color = grade)) + 
    geom_point() +
    labs(
      title = "Trump Approval Rating and Number of Tweets",
      subtitle = "Data from fivethirtyeight and Trump Twitter Archive",
      x = "Total Tweets",
      y = "Approval Rating"
    ) +
    theme_classic()
plot

# Here I calculate the correlation coefficient between the approval rating and
# the number of tweets

corr <- tibble %>% 
  summarize(corr = cor(total_tweets, approve))
corr
```

There does not seem to be a strong relationship in either direction between 
tweet activity and approval ratings. This is reflected by the scatterplot.



## Question 2: Run a multivariate regression

### 2A) Using lm()

```{r 2A, echo=FALSE}

# I'm interested in integrating grade as another variable to consider in the
# relationship between approval rating and number of tweets. We saw in the plot
# above that weeks with lower grades seem to fare better in approval rating than
# weeks with higher grades, regardless of the number of tweets. Toward multiple
# regression: here I use an ifelse condition to create a new variable “high_q”
# which takes a value of 1 if the poll is rated A+, A, or A-, and 0 if the
# rating is lower or missing.

tibble <- tibble %>% 
  mutate(high_q = ifelse(
    grade == "A+" |
    grade == "A" |
    grade == "A-", 
    1, 0)
  )

# Here I run a linear regression of approve on two variables: total_tweets and
# high_q. I tidy up the data immediately and select term, estimate, conf.low,
# and conf.high. I print a gt table with these values in a separate code chunk
# so that I will be able to access the original linear model itself if need be.
# I round to 5 decimal places for sufficient accuracy, using mutate_if() (from
# https://stackoverflow.com/questions/27613310/rounding-selected-columns-of-data
# -table-in-r).

tibble_lm <- tibble %>% 
  lm(approve ~ total_tweets + high_q, data = .) %>% 
  tidy(conf.int = TRUE) %>% 
  select(term, estimate, conf.low, conf.high)

tibble_lm_table <- tibble_lm %>% 
  mutate_if(is.numeric, ~ round(., 5)) %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Number of Tweets and Poll Quality on Reported Approval Rating",
    subtitle = "Data from fivethirtyeight and Trump Tweet Archive"
  ) %>% 
  cols_label(
    term = "Variable",
    estimate = "Estimate",
    conf.low = "Lower bound",
    conf.high = "Upper bound" 
  ) %>% 
  cols_align(align = "center")
tibble_lm_table
```


### 2B) Interpreting results

The estimated average treatment effect of high_q, i.e. the effect on approval
rating of changing the binary variable high_q from 0 to 1, is -2.34720. It seems
that, taking into account the other explanatory variable total_tweets, there is 
an associated decrease of on average 2.34720 points in reported approval rating
from switching from a low quality poll to a high quality poll. 

A frequentist intrepretation of the coefficients says that  ____________, while a Bayesian interpretation says that ___________. [FINISH]


### 2C) Interaction Variables

```{r 2C, echo=FALSE}

# We are now interested in investigating whether there might be a specific
# effect of more tweets on high quality polls, as opposed to looking at their
# effects on approval rating independently. Here I essentially copy-paste the
# code from 2B but run a new regression that includes total_tweets, high_q, and
# the interaction between total tweets and high quality.

new_lm <- tibble %>% 
  lm(approve ~ total_tweets * high_q, data = .) %>% 
  tidy(conf.int = TRUE) %>% 
  select(term, estimate, conf.low, conf.high)

new_lm_table <- new_lm %>% 
  mutate_if(is.numeric, ~ round(., 5)) %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Number of Tweets and Poll Quality on Reported Approval Rating",
    subtitle = "Data from fivethirtyeight and Trump Tweet Archive"
  ) %>% 
  cols_label(
    term = "Variable",
    estimate = "Estimate",
    conf.low = "Lower bound",
    conf.high = "Upper bound" 
  ) %>% 
  cols_align(align = "center")
new_lm_table
```


### 2D) Estimating Fitted Values

```{r 2D}

# From September 15 - September 19, 2017, Monmouth University ran a poll that
# was rated A+. That week, President Trump tweeted 84 times. Here I write out
# the formula that I would use to calculate the fitted value, or predicted
# approval rating for that poll, given my results in the interaction model from
# 2C. The value of high_q is 1 and the value of total_tweets is 84.
# estimated(approval rating) =

new_lm$estimate[1] + (new_lm$estimate[2] * 84) + (new_lm$estimate[3] * 1) +
  (new_lm$estimate[4] * -2.70146 * 1)

# I now check my work by recreating the (necessarily untidied) linear model from
# 2C and then pulling the relevant fitted value using the predict() function. I
# omit the customary echo=FALSE in order to print the code for both methods, for
# sake of comparison.

new_lm_untidied <- tibble %>% 
  lm(approve ~ total_tweets * high_q, data = .)

predict.lm(new_lm_untidied, newdata = tibble(high_q = 1, total_tweets = 84))
```

[the results are off by more than just a few decimal places! FINISH]


### 2E) Multiple Regression and the Rubin Causal Model

To interpret this multiple regression causually, we can consider each 
coefficient as the coefficient the treatment variable in turn, treating the 
other variables as confounding variables. However, the Fundamental Problem of
Causal Inference prevents us from justifying a causal interpretation of the
regression overall, since there are likely other confounding variables present.
The estimated coefficient on total_tweets is the effect that we anticipate on
approval rating for every additional tweet, taking into account the other
explanatory variable democrat (that is, holding democrat constant).
The coefficient on democrat is, similarly, the effect that we anticipate on
approval rating for every unit increase in the democrat variable, taking into
account the other explanatory variable total_tweets.
The coefficient on total_tweets:democrat defines the interaction effect, where 
the associated effect of total_tweets depends on the political party (Democrat 
vs. Republican). In other words, this coefficient measures any additional effect
on approval ratings beyond the individual effects of total_tweets and democrat.
This is an explanatory model since you are trying to determine how changes in 
tweet count and political party would change Trump's approval ratings.



## Question 3: Generalize to many regressions

```{r 3, echo=FALSE}

# First and foremost, I create a new variable "month" in both original datasets,
# in order to eventually be able to run a regression for each month. This code
# is expectedly similar to the code used to create the "week" variable.

poll$month <- ceiling(poll$week / 4)
tweets_summarized$month <- ceiling(tweets_summarized$week / 4)

# Now I initialize the dataset for plotting by filtering my poll data to the
# first 11 months

poll <- poll %>% 
  filter(month < 12)

# Now I create the graphs on the right-hand side as seen in the problem set
# instructions, using normal tidyverse functions (group_by, summarize, ggplot).
# First, the top right hand graph plots the average approval rating by month and
# poll quality. I create this graph using solely the poll dataset, recreating
# the high_q variable as before in order to provide an indicator of poll
# quality.

poll_plot <- poll %>% 
  mutate(high_q = ifelse(
    grade == "A+" |
    grade == "A" |
    grade == "A-", 
    1, 0)
  ) %>% 
  group_by(month) %>% 
  summarize(avg_approve = mean(approve)) %>% 
  ggplot(aes(x = month, y = avg_approve)) +
    geom_line(aes(color = poll$high_q)) +
    labs(
      title = "Approval Rating by Poll Quality",
      x = "Month",
      y = "Average Approval Rating"
    ) +
    theme_classic()

# Second, the bottom right hand graph plots the total number of tweets by month.
# I create this graph using solely the tweets_summarized tibble. 




```






